---
title: "Relative cont"
author: "Parker Bausman"
date: "2024-07-17"
output: html_document
---



##### SOMETHING FEELS OFF HERE. TRACE BACK TO NEMODWM2 AND TROUBLESHOOT 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(lubridate)
```

### This will be code to determine the relative contribution of nemo to subsidies. I am interested in how this varies at scale. I plan to look at a pond scale, nemo containing ponds, and all ponds sampled. I might even be able to estimate total cont across the whole cut. 

```{r}
#lets start with pond 1 since I Have the data prepped. 
#Ill use the emergence /m2 

pond1stuff$totalemerge <- NA
#total emergence per day 
pond1stuff$totalemerge <- rowSums(pond1stuff[ ,c(4,5)])
#percent cont. 
pond1stuff$percentcont <- NA

pond1stuff$percentcont <- (pond1stuff$Pond1NemoM2 / pond1stuff$totalemerge)*100
```

```{r}
ggplot(pond1stuff, aes(x=Date))+ 
  geom_point(aes(y = percentcont), size=2)+
  geom_line(aes(y = percentcont), size=.5)+ 
  labs(x= "Date", y= "Percent Contribution")+
  ggtitle("Nemo percent contribution to pond 1 export")+
  theme(plot.title = element_text(hjust = 0.5))+
  ylim(0,100)
```

```{r}
#Now lets do all 7 ponds 22

othervsnemo22$totalemerge22 <- NA
#total emergence per day 
othervsnemo22$totalemerge22 <- rowSums(othervsnemo22[ ,c(2,3)])
#percent cont. 
othervsnemo22$percentcont22 <- NA

othervsnemo22$percentcont22 <- (othervsnemo22$NemoM2022 / othervsnemo22$totalemerge22)*100
```

```{r}
ggplot(othervsnemo22, aes(x=Date))+ 
  geom_point(aes(y = percentcont22), size=2)+
  geom_line(aes(y = percentcont22), size=.5)+ 
  labs(x= "Date", y= "Percent Contribution")+
  ggtitle("Nemo percent contribution to sampled ponds export 2022")+
  theme(plot.title = element_text(hjust = 0.5))+
  ylim(0,100)
```
```{r}
#Now lets do all 7 ponds 23


othervsnemo23 <- data.frame(othervsnemo22[, c(1,4,5,10)])


othervsnemo23$percentcont23 <- NA

othervsnemo23$percentcont23 <- (othervsnemo23$NemoM2023 / othervsnemo23$totalemerge23)*100
```

```{r}

# Filter out NA values from the columns you are plotting
othervsnemo23_filtered <- othervsnemo23[complete.cases(othervsnemo23$percentcont23), ]


ggplot(othervsnemo23_filtered, aes(x=Date))+ 
  geom_point(aes(y = percentcont23), size=2)+
  geom_line(aes(y = percentcont23), size=.5)+ 
  labs(x= "Date", y= "Percent Contribution")+
  ggtitle("Nemo percent contribution to sampled ponds export 2023")+
  theme(plot.title = element_text(hjust = 0.5))+
  ylim(0,100)
```

#when we think about scale a single pond may provide a large sub contribution but at scale this contribution is smaller but over a longer period 
